---
title: "intro"
author: '19031'
date: "12/31/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to SC19031}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__SC19031__ is a simple R packag and it is based on the specific application of the DBSCABN(Density-based spatial clustering of applications with noise) clustering algorithm. It initially classifies the target data and further lists all types of data.
Also included in this file are the answers to all assignments by the author when he took the course in statistical calculation.



##__Fdbscan__


Fdbscan is a method for preliminary clustering of given data based on DBSCAN algorithm.

```{r}
Fdbscan<-function(data,eps,M){
  N<-length(data[,1])
  Eu<-as.matrix(dist(data,diag = TRUE))
  colnames(Eu)<-NULL
  rownames(Eu)<-NULL
  I<-c(1:N)
  k<-1
  m<-numeric(N)
  for (i in 1:N) { m[i]<-0
  }
  while(length(I) > 0){
    i <- sample(I,1)
    I <- I[- which( I==i) ]
    T <- c(which(Eu[i,] <= eps ))
    if(m[i] == 0)
      if(length(T) < M)
        m[i] <- -1
    else
      m[i] <- k
    while(length(T) > 0 ){
      j <- sample(T,1)
      T <- T[ - which(T == j)]
      if(m[j]!= 0 & m[j] != -1)
        m[j] <- m[j]
      else{ m[j]<- k
      if(length(c(which(Eu[j,] > eps ))) >= M)
        T <-union(T, c(which(Eu[j,] <= eps )))
      else
        m[j]<- m[j] }
    }
    k<-k+1
  }
  return(m) }

##__Examle__

data1<-iris[,1:2]
m1<-Fdbscan(data1,0.25,3)
m1
table(m1)
data2<-iris[,1:3]
m2<-Fdbscan(data2,0.3,3)
m2
table(m2)
```





##__CLuster__


Further processing of data based on Fdbscan method.

```{r}
CLuster<-function(data,m,M){
  colnames(data)<-NULL
  rownames(data)<-NULL
  table1<-table(m)
  N_1<-as.numeric(rownames(table1))
  rownames(table1)<-NULL
  Ind1<-which(table1>=M)
  K<-length(Ind1)
  CLuster<-list()
  for (j in 1:K) {
    CLuster[[j]]<-data[which(m==N_1[Ind1[j]],arr.ind = TRUE),]
  }
  return(CLuster)
}

##__Examle__

data1<-iris[,1:2]
m1<-Fdbscan(data1,0.25,3)
z1<-CLuster(data1,m1,3)
z1
data2<-iris[,1:3]
m2<-Fdbscan(data2,0.3,3)
z2<-CLuster(data2,m2,3)
z2
```





